---
title: "STA279_Lab1"
author: "Sherry Mao"
date: "2/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
grad_app <- read.csv("https://stats.idre.ucla.edu/stat/data/binary.csv")
```



## Question 1

```{r}
library(tidyverse)
glimpse(grad_app)
```

(Type your answer to question 1 here)
400 students are in the data. 

## Question 2

```{r}
grad_app_no_na <- grad_app %>%
  drop_na()
glimpse(grad_app_no_na)
```

(Type your answer to question 2 here)
400 students are in grad_app_no_na. There are no missing values in the original data because the students stay 400 after dropping NAs.

## Question 3

```{r}
grad_app_prestigious <- grad_app %>%
  filter(rank == 1)
glimpse(grad_app_prestigious)
```

(Type your answer to question 3 here)
There are 61 students attended the most prestigious school. 

## Question 4

```{r}
grad_app %>%
  ggplot(aes(x = admit)) +
  geom_bar() +
  labs(x = "Accepted to grad school?",
       title = "Bar chart of grad school acceptance") +
  theme_bw()
```

## Question 5

```{r}
grad_app %>%
  ggplot(aes(x = gpa)) +
  geom_histogram() +
  labs(x = "GPA of applicants",
       title = "Histogram of grad school applicants") +
  theme_bw()
```

(Type your answer to question 5 here)


## Question 6

```{r}
grad_app %>%
  summarize(standard_deviation_gpa = sd(gpa),
            mean_gpa = mean(gpa))
```


## Question 7

```{r}
class(grad_app$admit)
```

(Type your answer to question 7 here)
The admit is an integer variable. 


## Question 8

```{r}
#mutate function modifies column to create new column
grad_app <- grad_app %>%
  mutate(admit = as.factor(admit))
class(grad_app$admit)
#side by side boxplot between acceptance and gpa
grad_app %>%
  ggplot(aes(x = admit, y = gpa)) +
  geom_boxplot() +
  labs(x = "Acceptance to grad school",
       y = "GPA",
       title = "Acceptance to grad school versus GPA") +
  theme_bw()
```


## Question 9

```{r}
#group_by function
grad_app %>%
  group_by(admit) %>%
  summarize(median_gre = median(gre),
            iqr_gre = IQR(gre))
#mean and sd
grad_app %>%
  group_by(admit) %>%
  summarize(mean_gre = mean(gpa),
            sd_gre = sd(gpa))
```


## Question 10

(Type your answer to question 10 here)
There is a strong positive correlation between students gpa and acceptance to grad schools. 


## Question 11

```{r}
table(grad_app$rank, grad_app$admit)
```

(Type your answer to question 11 here)
probability: 33/61 = 0.54
odds: 0.54/(1-0.54) = 1.17


